submission_4

### 2023-07-19 submission_4/submission_4.qmd
Adds sources for subission 4

#

>>>>

# Submission 4: TLS and Sentinel 2 comparison

## General study concept and conditions

The purpose of this document is the comparison of terrestial laser/LiDAR scanning and Sentinel 2 (satellite) data of the same spot.

**Insert some description and the data of the plot. I wasn't there, so probably someone else should do it**

## Algorithm idea

## Results

This section lists, describes and tries to explain the plots and graphs generated by the algorithm described in the previous section.

### Tree height statistic comparison

In this section the general measurements are compared.

*First the general heigths:*

![Height calculation of TLS (resampled to resolution of the sentinel data)](TLS_plots/figures/chm_height.png)

### Residual computation

In this section we compute the residuals of the
